Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-22 prop_iop.tex
prop_letter.tex Updating Kochen-Specker interpertation...

\begin{lemma}\label{lemma:deterministic-CIVPM}Consider a sample
space~$\Omega$ with $d$ elements, and $\delta<1/d$. Given a $\delta$-deterministic
CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, the following statements
are true:
\begin{enumerate}
\item If $\bar{\mu}$ is $0$-deterministic, its left-end~$\mul$ and right-end~$\mur$
are the same CRVPM, and will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
\item There is a unique element~$\omega_{0}\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)\subseteq\left[1-\delta,1\right]$,
denoted by $\bar{\mu}^{-1}\left(\left[1-\delta,1\right]\right)$.
In particular, if $\bar{\mu}$ is $0$-deterministic, $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\left\{ \pmeas\left(\left\{ \omega_{0}\right\} \right)\right\} =\necess$,
denoted by $\pmeas^{-1}\left(1\right)$ or $\bar{\mu}^{-1}\left(\necess\right)$.
\end{enumerate}
\end{lemma}

\begin{proof}~
\begin{enumerate}
\item The directly consequence of lemma~\ref{lemma:QIVPM2QCM}.
\item We have either $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[1-\delta,1\right]$.
\begin{casenv}
\item If $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,\delta\right]$
for all $\omega\in\Omega$, then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,d\delta\right]\Rightarrow d\delta>1$.
A contradiction!
\item If there are more than one~$\omega\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[1-\delta,1\right]$,
then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[2-2\delta,d\right]\Rightarrow2\delta>1$.
A contradiction!
\end{casenv}
Therefore, there is a unique element~$\omega_{0}\in\Omega$ such
that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)\subseteq\left[1-\delta,1\right]$.
\end{enumerate}
\end{proof}

@@

>>>>

\begin{lemma}\label{lemma:deterministic-CIVPM}Consider a sample
space~$\Omega$ with $d$ elements, and $\delta<1/d$. Given a $\delta$-deterministic
CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, the following statements
are true:
\begin{enumerate}
\item If $\bar{\mu}$ is $0$-deterministic, its left-end~$\mul$ and right-end~$\mur$
are the same CRVPM, and will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
\item There is a unique element~$\omega_{0}\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)\subseteq\left[1-\delta,1\right]$,
denoted by $\bar{\mu}^{-1}\left(\left[1-\delta,1\right]\right)$.
In particular, if $\bar{\mu}$ is $0$-deterministic, $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)=\left\{ \pmeas\left(\left\{ \omega_{0}\right\} \right)\right\} =\necess$,
$\omega_{0}$ could be denoted by $\pmeas^{-1}\left(1\right)$ or
$\bar{\mu}^{-1}\left(\necess\right)$.
\end{enumerate}
\end{lemma}

\begin{proof}~
\begin{enumerate}
\item The direct consequence of lemma~\ref{lemma:QIVPM2QCM}.
\item We have either $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,\delta\right]$
or $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[1-\delta,1\right]$.
\begin{casenv}
\item If $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,\delta\right]$
for all $\omega\in\Omega$, then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[0,d\delta\right]\Rightarrow d\delta\ge1$.
A contradiction!
\item If there are more than one~$\omega\in\Omega$ such that $\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[1-\delta,1\right]$,
then $\necess=\bar{\mu}\left(\Omega\right)\subseteq\sum_{\omega\in\Omega}\bar{\mu}\left(\left\{ \omega\right\} \right)\subseteq\left[2-2\delta,d\right]\Rightarrow2\delta\ge1$.
A contradiction!
\end{casenv}
Therefore, there is a unique element~$\omega_{0}\in\Omega$ such
that $\bar{\mu}\left(\left\{ \omega_{0}\right\} \right)\subseteq\left[1-\delta,1\right]$.
\end{enumerate}
\end{proof}

@@

\begin{lemma}\label{lemma:deterministic-QIVPM}Given a Hilbert space
of dimension~$d$, $\delta<1/d$, and a $\delta$-deterministic QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$,
the following statements are true:
\begin{enumerate}
\item If $\bar{\mu}$ is $0$-deterministic, its left-end~$\mul$ and right-end~$\mur$
are the same QRVPM, and will be simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
\item Given an orthonormal basis~$\Omega$, there is a unique element~$\ket{\psi_{i_{0}}}\in\Omega$
such that $\bar{\mu}\left(\proj{\psi_{i_{0}}}\right)\subseteq\left[1-\delta,1\right]$,
denoted by $\bar{\mu}^{-1}\left(\left[1-\delta,1\right]\right)\cap\Omega$.
In particular, if $\bar{\mu}$ is $0$-deterministic, $\bar{\mu}\left(\proj{\psi_{i_{0}}}\right)=\left\{ \pmeas\left(\proj{\psi_{i_{0}}}\right)\right\} =\necess$,
$\proj{\psi_{i_{0}}}$ could be denoted by $\pmeas^{-1}\left(1\right)\cap\Omega$
or $\bar{\mu}^{-1}\left(\necess\right)\cap\Omega$.
\end{enumerate}
\end{lemma}

\begin{proof}~
\begin{enumerate}
\item The direct consequence of lemma~\ref{lemma:QIVPM2QCM}.
\end{enumerate}
\end{proof}

### 2017-09-22 prop_letter.tex
prop_letter.tex Updating Kochen-Specker interpertation...

The natural KS assumption in 0-deterministic QIVPM is the following
one correspondence of Condition~\ref{cond:sum-one}.

@@

\noindent Notice that the expectation value relative to $0$-deterministic
$\bar{\mu}$ plays the same role as the hidden variable assignment~$v$
in the original Kochen-Specker theorem. After we proved these two
conditions, we can easily follow Mermin to build a contradiction.

>>>>

The natural KS assumption in 0-deterministic QIVPM is the one corresponding
to Condition~\ref{cond:sum-one}.

@@

\noindent After we proved these two conditions, we can easily follow
Mermin's proof to build a contradiction. Notice that the expectation
value relative to $0$-deterministic $\bar{\mu}$ plays the same role
as the hidden variable assignment~$v$ in the original Kochen-Specker
theorem despite their physical meanings are not exactly the same.
